Group Fou\\*R* Term Project - Summary of Raw Data, Explanations and Preliminary Analysis

### 2018-12-16 Draft.Rmd
.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
```

@@

```{r}
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))

@@

```{r}
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

@@

#Export percentage of Countries

@@

@@

```{r}
ggplot(table, aes(x=year)) +
  geom_point(aes(y=value, color=Country, shape=variable), size=4) + 
  facet_grid(~variable) +
   labs(title="YoY Total Value Change",
    x="Year",
    y="% Change in  Value",
    shape=c("Trade Type"))
```

@@

mean(summarytableCanadaEx$ExpChngYoy)
median(summarytableCanadaEx$ExpChngYoy)
sd(summarytableCanadaEx$ExpChngYoy)
quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - IQR
ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + IQR

@@

mean(summarytableCanadaIm$ImpChngYoy)
median(summarytableCanadaIm$ImpChngYoy)
sd(summarytableCanadaIm$ImpChngYoy)
quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - IQR
ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + IQR

@@

mean(summarytableRussianEx$ExpChngYoy)
median(summarytableRussianEx$ExpChngYoy)
sd(summarytableRussianEx$ExpChngYoy)
quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - IQR
ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + IQR

@@

mean(summarytableRussianIm$ImpChngYoy)
median(summarytableRussianIm$ImpChngYoy)
sd(summarytableRussianIm$ImpChngYoy)
quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - IQR
ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + IQR

@@

@@

grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
grid.arrange(plotRusEx, plotRusIm,  nrow = 2)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(gridExtra)
library(lubridate)
library(plotrix)
```

@@

@@

```{r}
ttable1=export_jTableMELTED%>%group_by(Country)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))

exptable1=export_jTableMELTED%>%group_by(Country)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))

pex1_table<-ttable1%>%
  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
  select(Country,co_total,perc_count)

imptable1=import_jTableMELTED%>%group_by(Country)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))

pim1_table<-imptable1%>%
  mutate(perc_count=(co_total/sum(ttable1$co_total))*100)%>%
  select(Country,co_total,perc_count)

lbls_i <- paste(pim1_table$Country,round(pim1_table$perc_count,1)) # add percents to labels
lbls_i <- paste(lbls_i,"%",sep="") # ad % to labels

pie3D(pim1_table$perc_count,labels=lbls_i,main = "Total Percentage Import Per Countries", explode=0.1, radius=.9,
      labelcex = 1.2, start=0.7)

lbls_e <- paste(pex1_table$Country,round(pex1_table$perc_count,1)) # add percents to labels
lbls_e <- paste(lbls_e,"%",sep="") # ad % to labels

pie3D(pex1_table$perc_count,labels=lbls_e,main = "Total Percentage Export Per Countries", explode=0.1, radius=.9,
             labelcex = 1.2, start=0.7)

```{r}
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

#Import & Export percentage of Countries

@@

@@

We drilled down the analysis for the countries which decreases the average, namely China, Russia and Germany. For this aim, we build up shiny app to review the products by defining the Country and ratio showing cumulative percentage of share of products over total import value of this country.

Please follow the link for interactive graph: [Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)

Through the shiny app, it is understood that
.70% of import value from China is coming from 8 products 
.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
.%70 is from commodities and mineral fuels for import from Russia
.only commodities constitute 43% of total import of Russia
.vehicles other than railway is the top product imported from Germany
.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles

IMAGE

###OMER2

@@

```{r, }
ggplot(table, aes(x=year)) +
  geom_point(aes(y=value, color=Country, shape=variable), size=4) + 
  facet_grid(~variable) +
   labs(title="YoY Total Value Change",
    x="Year",
    y="% Change in  Value",
    shape=c("Trade Type"))
```

@@

mean(summarytableCanadaEx$ExpChngYoy)
median(summarytableCanadaEx$ExpChngYoy)
sd(summarytableCanadaEx$ExpChngYoy)
quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableCanadaIm$ImpChngYoy)
median(summarytableCanadaIm$ImpChngYoy)
sd(summarytableCanadaIm$ImpChngYoy)
quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableRussianEx$ExpChngYoy)
median(summarytableRussianEx$ExpChngYoy)
sd(summarytableRussianEx$ExpChngYoy)
quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableRussianIm$ImpChngYoy)
median(summarytableRussianIm$ImpChngYoy)
sd(summarytableRussianIm$ImpChngYoy)
quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

```{r, fig.height = 8, fig.width = 16}

@@

grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
